Quantum Computing and its Implications on Digital Security

### 2021-12-12 paper.tex
feat: Add martinis citation

Martinis and Osborne state that Josephson junction quantum computers are especially interesing because superconductor could provide long coherence times and because increasing the number of qubits should be straightforward.

>>>>

Martinis and Osborne state \cite{martinis} that Josephson junction quantum computers are especially interesing because superconductor could provide long coherence times and because increasing the number of qubits should be straightforward.
